### 2015-01-29 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated Report

WATER DISTRIBUTION

Purpose:
- Determine the appropriate location for nozzles
- Determine water distribution

Setup:
Task Force Tips Metro 1, Fixed Gallonage (120 gpm)
Straight Stream
30 degree Fog
7/8” Smooth Bore
100 ft of 1-3/4 inch hose

The hose streams were from fixed monitor nozzles simulating a firefighter with the hose line in the structure.

Controlled and operated via a gate valve from the exterior.

12 Experiments:
4 SS from room
2 Fog from room
2 SS from Hall
2 Fog from Hall
1 SB from Hall
1 SB from Room

2.5 square foot collector bin.

Bins were poly boxes with interlacing lips to prevent water from going in between.

Measured how much of the water ended up in what part of the room.

The building was sheathed in plastic for the water flow tests as to protect and preserve the structure before any fire suppression tests were conducted.

@@

Room and contents fire inside structure
Two points of interior attack
- Remotely activated in hallway (indirect attack)
- Remotely activated in fire room (direct attack)

Common household furnishings.

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of teach structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

>>>>

The experimental set-up for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.

SPRAY DENSITY MEASURES

Thirty two tests were conducted to determine spray density measures based on various nozzle patterns and locations. The purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures. The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles. This set-up is representative of a firefighter operating on a hose line within the structure. Therefore, it is critical to ensure proper nozzle location for the tests to follow to provide the most realistic test conditions.

The nozzles chosen for these experiments were as a result of those available through the MCFRS provided engine and decided upon during the CAFS workshop.  This test series used Task Force Tips (TFT) Metro 1, Fixed Gallonage nozzles with a flow rate of 120 gpm. These are automatic nozzles which have a 7/8 inch slug-tip and can be varied from a straight stream to a wide fog for application. The set-up also included 100 ft of 1-3/4 inch hose.  The nozzles were mounted to a "blitz-fire" monitor device and placed inside the structures.  The nozzles were controlled and operated via a gate valve from the exterior.

The tests conducted for spray density measurement were divided between the available structures at the Delaware County ESTC. Twenty one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests. The tests varied by changing the nozzle height and location within the structure. Additionally, the nozzle pattern was varied as well. A description and drawings of these facilities can be seen in the Experimental Facility section below.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Flows}
	\caption{Spray Density Nozzle Patterns}
	\label{fig:Spray_Density_Nozzle_Patterns}
\end{figure}

The experiments were conducted by placing interlocking collector bins across the floor surface area of the burn rooms within each structure. Each collector bin was a 2.5 square foot poly box. The building was sheathed in plastic for the spray density tests in order to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. The nozzles were flowed for a set duration and once the test was concluded, the bins were removed from the structure.  The amount of water in each bin was measured in order to determine how much of the water ended up in each part of the room dependent on the nozzle location and pattern. The results can be seen in the sections to follow.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
	\label{fig:Spray_Density_Set_Up}
\end{figure}

GAS LAYER COOLING

@@

The fire suppression analysis included a series of 14 tests in two single story experimental structures, also located on the grounds of the Delaware County ESTC. Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent. Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings. The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used. Several other factors including the fuel load and available ventilation were varied during these tests.

Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.  The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.  The fires were intended to replicate room and contents fires typically seen within residential structures.  The hose lines were pre-deployed with fixed nozzles set in two locations.  One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle). The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room. Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack. The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.  This position represented a direct interior attack.

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
	\caption{Hallway Nozzle Location}
	\label{fig:Hallway_Nozzle_Location}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
	\caption{Room Nozzle Location}
	\label{fig:Room_Nozzle_Location}
\end{figure}

@@

Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

@@

Each 
12 Experiments:
4 SS from room
2 Fog from room
2 SS from Hall
2 Fog from Hall
1 SB from Hall
1 SB from Room
